Model based reinforcement learning at FERMI FEL

### 2020-11-16 main.tex
txs auto checkin

\begin{figure}[!h]
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/MBRL_overview}
	\caption{A schematic overview of the AE-Dyna approach used in this paper.}
	\label{fig:MBRL_overview}
\end{figure}
\subsection{Critical design decisions}
In the following the most important aspects of a successful application of a Dyna-AE algorithm are listed:
\begin{itemize}
	\item The ANN - including the prior - number of models - noise level - early stopping
	\item The number of data points and the policy.
	\item The uncertainty - how is this included?
	\item The episodic design - avoid long trajectories.
	\item The MFRL agent as e.g. the TRPO and PPO or the SAC.
\end{itemize}
We try to discuss all items in some detail in the following.
The anchoring ensemble methods usually yields good results already with a small number of different networks. The idea behind it, is to mimic the posterior probability of the dynamics model to capture first of all its own uncertainty due to the lack of data. Empirical results show that three to five models were sufficient to see clear advantages over a single network approach and the main goal is not to calculate the exact posterior of the model. A small two-layer network with around 15-25 nodes and the $tanh$ activation were used. The last layer was linear and the inputs were normalized to the interval [-1,1]. The prior is controlled by the initialization of the weights, which were normalized by the number of nodes in each layer. The noise level is also respected during the initialization. For the moment only homeoscetastic errors are used. Several methods to set the training method were implemented. Early stopping, a standard techniques showed good results, mainly to the fact, that the number of training steps is increasing with more data. The advantage is that the uncertainty at regions without data are shrink in this way. A fixed loss value threshold was also tested, as also used in the original anchore-ensemble technique. In the experiments a combination of both was taken.\\
One of the most crucial points is how this uncertainties are taken into account by the RL algorithms. Several different approaches were tried. It is possible to take the average of the models and add Gaussian noise leveled by the standard deviation of the models. Another straight forward way is to randomly select a model to provide at each training step, which is the original implementation of the ME-TRPO algorithm and was used in the experiments labeled \it{ME-TRPO}. A pessimistic setting only would select the model resulting in the lowest predicted reward. Good results were obtained by following a randomly selected single model each full episode and were used in the experiments labeled \it{AE-Dyna}.

>>>>

\begin{figure}[!h]
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/MBRL_overview}
	\caption{A schematic overview of the AE-Dyna approach used in this paper.}
	\label{fig:MBRL_overview}
\end{figure}
\subsection{Critical design decisions}
In the following the most important aspects of a successful application of a Dyna-AE algorithm are listed:
\begin{itemize}
	\item The ANN - including the prior - number of models - noise level - early stopping
	\item The number of data points and the policy.
	\item The uncertainty - how is this included?
	\item The episodic design - avoid long trajectories.
	\item The MFRL agent as e.g. the TRPO and PPO or the SAC.
\end{itemize}
We try to discuss all items in some detail in the following.
The anchoring ensemble methods usually yields good results already with a small number of different networks. The idea behind it, is to mimic the posterior probability of the dynamics model to capture first of all its own uncertainty due to the lack of data. Empirical results show that three to five models were sufficient to see clear advantages over a single network approach and the main goal is not to calculate the exact posterior of the model. A small two-layer network with around 15-25 nodes and the $tanh$ activation were used. The last layer was linear and the inputs were normalized to the interval [-1,1]. The prior is controlled by the initialization of the weights, which were normalized by the number of nodes in each layer. The noise level is also respected during the initialization. For the moment only homeoscetastic errors are used. Several methods to set the training method were implemented. Early stopping, a standard techniques showed good results, mainly to the fact, that the number of training steps is increasing with more data. The advantage is that the uncertainty at regions without data are shrink in this way. A fixed loss value threshold was also tested, as also used in the original anchore-ensemble technique. In the experiments a combination of both was taken.\\
One of the most crucial points is how this uncertainties are taken into account by the RL algorithms. Several different approaches were tried. It is possible to take the average of the models and add Gaussian noise leveled by the standard deviation of the models. Another straight forward way is to randomly select a model to provide at each training step, which is the original implementation of the ME-TRPO algorithm and was used in the experiments labeled \emph{ME-TRPO}. A pessimistic setting only would select the model resulting in the lowest predicted reward. Good results were obtained by following a randomly selected single model each full episode and were used in the experiments labeled \emph{AE-Dyna}.
